---
title: 'Lab 3: Exploring Discrete Probability Distributions'
author: "Corey Katz"
date: "due:Oct 16, 2019 5:00 pm"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, include=FALSE}
library(tidyverse)
```



## Bernoulli and Binomial Distributions

Functions `dbinom`,`pbinom`,`qbinom`,`rbino`

### Binomial

Taken from Open Intro Exercise 4.17:

Data collected by the Substance Abuse and Mental Health Services Administration (SAMSHA) suggests that 69.7% of 18-20 year olds consumed alcoholic beverages in any given year. A random sample of 10 people age 18-20 was taken. 

Write text below:

1. What distribution does the number of 18-20 that consumed alcohol follow?

Binomial distribution.

2. What is the expected value of this distribution?

```{r}
n1 <- 10
p1 <- 0.697

n1*p1
```


6.97.

3. What is the variance of this distribution?

```{r}
n1*p1*(1-p1)
```

The variance is 2.11.

\newpage

Write code below:

4. What is the probability that exactly 5 out of 10 18-20 year olds have consumed an alcoholic beverage?

```{r}
dbinom(x=5,size=10,prob=0.697)
```

The probability is 0.11.

5. What is the probability that at most 3 out of 10 randomly sampled 18-20 year olds have consumed
alcoholic beverages?

```{r}
pbinom(q=3,size=10,prob = 0.697)
```

The probability is 0.01.

6. What is the probability that at least 6 out of 10 randomly sampled 18-20 year olds have consumed
alcoholic beverages?

```{r}
1-pbinom(q=5, size=10, prob=0.697)
```

The probability is 0.84

7. What is the median of this distribution?

```{r}
qbinom(p=0.5, size=10, prob=0.697)
```

The median is 7.

You can also randomly generate samples using a binomial distribution.

```{r}
rbinom(n=100,size = 20,prob = 0.5)
```


\newpage

## Geometric Distribution

Functions `dgeom()`,`pgeom()`,`qgeom()`,`rgeom()`

# In R, these functions model differently than the book. This looks at the number of failures until the first success.

The probability of a defective lightbulb at a certain factor is 0.30. 
Write text here:

8. What is distribution would the number of bulbs until the first defective is found follow?

Geometric


9. What is the expected number of lightbulbs that are checked before finding a defective bulb?

```{r}
1/0.3
```



10. What is the probability that the tenth lightbulb is the first defective bulb?

```{r}
dgeom(x=9, prob = 0.3)
```




11. What is the probability that the first defective bulb is found after the first 3 bulbs are checked?

```{r}
1-pgeom(q=3,prob=0.3)

```



12. Again we can draw a random sample:

```{r}
rgeom(100,0.3)
```

